Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-09 R0V0.tex
Remove the need for the definition of SDD matrices. Add condition for the vector fields to be polynomials

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the search for the matrix $F$ is restricted to have some structure on the diagonal, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.

\begin{definition}\label{def:SDD}
	A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.
\end{definition}

@@

Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be cast into the following programming
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rl}
SDSOS_l:=\underset{}{\min} & t^2 \\
\text{subject to} &  -F_l\in\mathbf{SDD}(U_l)
\end{array}
\end{equation}
which consists of verifying the feasibility $-F_l\in\mathbf{SDD}(U_l)$, where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
Note that, when the requirement of $A$ is diagonally dominant can be interpreted as the network having a weak coupling.

@@

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N\dfrac{N+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.

@@

In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.

@@

For each $j\in\mathbb{N}$, $\mathbf{C}_j$

>>>>

Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the vector fields $f$ and $B$ are polynomials and the search for the matrix $F$ is restricted to have appropriate diagonal structure, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.

A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.

@@

Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rcl}
-F_l&\in&\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
Note that, when the requirement of $A$ is diagonally dominant can be interpreted as the network having a weak coupling.

@@

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N\dfrac{N+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

@@

In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. The sets $\mathbf{C}_j$, $j\in\mathbb{N}_{[1,8]}$, are defined as
\begin{equation*}
	\begin{array}{rcl}
		\mathbf{C}_1=\mathbf{C}_2=\begin{bmatrix}1, 1, 0, 0\end{bmatrix}^\top
	\end{array} 
\end{equation*}

@@

For each
